### 2013-04-27 doc/dissertation/document/chapters/spn_equations/spn_equations.tex
more dissertation refactoring

\chapter{The Simplified $P_N$ Equations}
\label{ch:spn_equations}

@@

\subsection{Preconditioning Strategy}
\label{subsec:spn_preconditioning}
If Monte Carlo methods are to be used to solve the $SP_N$ system of
equations, a different preconditioning strategy is required in order
to ensure convergence for systems of all $SP_N$ and $P_N$ orders with
arbitrary energy group structures. To achieve this, we look back to
the sparsity plots we generated in Figures~\ref{fig:group1},
\ref{fig:group10ds} and \ref{fig:group10us} as well as the multigroup
$SP_N$ equations. Initially, the diagonal character of the system led
us to try point Jacobi preconditioning with only marginal
results. From the sparsity plots we note the block structure that
ultimately arises from the multigroup scattering matrices and their
insertion into Eq~(\ref{eq:A_block_matrix}). When full upscatter and
downscatter are used the resulting blocks are completely dense while
only downscatter gives a lower triangular scattering matrix and the
block structure shown in Figure~\ref{fig:group10ds}.

@@

>>>>

\chapter{Monte Carlo Solution Methods for the Simplified $P_N$ Equations}
\label{ch:spn_equations}

@@

\subsection{Block Jacobi Preconditioning}
\label{sec:spn_preconditioning}
If Monte Carlo methods are to be used to solve the $SP_N$ system of
equations, a different preconditioning strategy is required in order
to ensure convergence for systems of all $SP_N$ and $P_N$ orders with
arbitrary energy group structures. To achieve this, we look back to
the sparsity plots we generated in Figures~\ref{fig:group1},
\ref{fig:group10ds} and \ref{fig:group10us} as well as the multigroup
$SP_N$ equations. Initially, the diagonal character of the system led
us to try point Jacobi preconditioning with only marginal
results. From the sparsity plots we note the block structure that
ultimately arises from the multigroup scattering matrices and their
insertion into Eq~(\ref{eq:A_block_matrix}). When full upscatter and
downscatter are used the resulting blocks are completely dense while
only downscatter gives a lower triangular scattering matrix and the
block structure shown in Figure~\ref{fig:group10ds}.

@@

%%---------------------------------------------------------------------------%%
\section{Fuel Assembly Criticality Calculations}
\label{sec:fuel_assembly_calcs}

\subsection{Jacobi Preconditioned Calculations}
\label{subsec:jacobi_prec_assembly_calc}

\subsection{MCSA Break Down}
\label{subsec:mcsa_break_down}

\subsection{Advanced Preconditioning Strategies}
\label{subsec:spn_advanced_preconditioning}

\subsubsection{ILUT Preconditioning}
\label{subsubsec:spn_ilut_preconditioning}

\subsubsection{Sparse Approximate Inverse Preconditioning}
\label{subsubsec:spn_spainv_preconditioning}

\subsubsection{SPAINV Improved ILUT Preconditioning}
\label{subsubsec:spn_spainv_preconditioning}

\subsection{MCSA Comparison to Conventional Methods}
\label{subsec:spn_comparison}
